Predicting Solid State Material Platforms for Quantum Technologies

### 2022-03-30 predictingQT.tex
update

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{physics}
\usepackage{lipsum}
% \usepackage{subfig} %not compatible with subcaption
% \usepackage{braket}
\usepackage{siunitx}
\usepackage{color}
% \usepackage{caption}
\usepackage{subcaption}
\usepackage{tikz,pgfplots}
\usepgfplotslibrary{groupplots,dateplot}
\usetikzlibrary{patterns,shapes.arrows}
\usepackage{makecell}
\captionsetup[table]{skip=10pt}
\pgfplotsset{compat=1.17}
\sisetup{separate-uncertainty}
\usepackage{hyperref} 
% \usepackage{longtable}
\usetikzlibrary{patterns,shapes.arrows, arrows.meta,bending, shapes,calc,fadings,decorations.pathreplacing,positioning,arrows.meta}
\pgfplotsset{compat=newest}

@@

%Figure 1 introduction schematic 
\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\textwidth]{figures/ht-workflow-new-2.png}
    \caption{Schematic of an example workflow in material informatics. Results from theory, experiment and computation are fed into material databases (arrow pointing to the center). A cycle involving material screening, machine learning and predictions leads to knowledge gain and ultimately applications in fields such as clean energy and quantum technology. 
    }
    \label{fig:ht-workflow}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\textwidth]{figures/flow_chart_2.png}
    \caption{The project workflow starting from an initial Materials Project (MP) query, and ending with a featurized dataset with entries from several other databases. 
    To limit the memory and computational usage, the data are partitioned into smaller subsets where the respective Pymatgen objects (Pymatgen is a robust, open-source Python library for materials analysis \cite{pymatgen}) are obtained through a query to be used in the following featurization steps. This process is repeated iteratively until all the data has been featurized. \emph{DOS} refers to density of states and \emph{band} to the electronic band structure. 
    }
    \label{fig:flowchart}
\end{figure}

@@

\begin{figure}[t] %!htp
    \centering
    \begin{subfigure}{1\textwidth}
        \centering
        \scalebox{0.85}{\input{figures/parallel-coordinates-plots/01-ferrenti-approach-v2.pgf}}
    \end{subfigure}
    \begin{subfigure}{1\textwidth}
        \centering
          \scalebox{0.85}{\input{figures/parallel-coordinates-plots/02-extended-ferrenti-approach-v3.pgf}}
    \end{subfigure}
    \begin{subfigure}{1\textwidth}
        \centering
          \scalebox{0.85}{\input{figures/parallel-coordinates-plots/03-empirical-approach-v3.pgf}}
    \end{subfigure}
    \caption{Parallel coordinate plots for the different approaches. To limit data cluttering, we have randomly collected up to $250$ entries for each class. For the empirical approach, we have used all the $187$ suitable candidates. The axes show total magnetization (mag), space group (SG), ionic character (ionic char), covalent range (cov range) as calculated from elemental properties, number of elements (num elements) and energy gap (Eg) as extracted from the MP database.} 
    \label{fig:parallel-coordinates-approaches}
\end{figure}

\begin{figure}%[h] %!tbp
    \centering
    \begin{subfigure}{0.35\textwidth}
        \centering
        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/01-ferrenti-approach.pdf}
    \end{subfigure}%
    \begin{subfigure}{0.35\textwidth}
        \centering
        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/02-augmented-ferrenti-approach.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \centering
        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/03-insightful-approach.pdf}
    \end{subfigure}
    \caption{Two-dimensional scatter plots for the three different approaches. We have identified the eigenvectors corresponding to the two largest eigenvalues of the covariance-matrix, that is, the two most important principal components of the initial data from the Materials Project query. Then, we have transformed the sets of labeled data resulting from the three approaches and visualized them as scatter plots. Green squares display suitable candidates, along with the black (SiC), blue (diamond) and yellow (Si) symbols in the bottom panel, and red triangles represent unsuitable candidates.}
    \label{fig:2dscatterplotpca}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \input{figures/feature-importance/01-ferrenti-approach-PC-v2.tex}
        \label{fig:01-fi-e}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \input{figures/feature-importance/01-ferrenti-approach-GB-v2.tex}
        \label{fig:01-fi-d}
    \end{subfigure}%
    \hfill
    \begin{subfigure}[b]{0.45\textwidth}
        \input{figures/feature-importance/03-empirical-approach-PC-v2.tex}
        \label{fig:03-fi-e}
        \subcaption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \input{figures/feature-importance/03-empirical-approach-GB-v2.tex}
        \label{fig:03-fi-d}
        \subcaption{}
    \end{subfigure}
    \caption{Visualization of different parameters for the $25$ most principal components ranked in descending order by (a) the explained variance for the Ferrenti (upper panel) and empirical (lower panel) approaches, and (b) the gradient boosting coefficients for the corresponding approaches. Note that in (a) we visualize only the results of the PCA analysis while in (b) there are results of the PCA reduced training sets using gradient boosting \cite{Hastie2009,xgboost2016}. The latter shows that for the empirical approach most of the physics is represented by a few features. The results in (b) are similar to those obtained with logistic regression, decision trees and random forests.  
    }
    \label{fig:PComponents}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.85\textwidth]{figures/vesta-images/fig6-all.png}
    \caption{Illustrations of the crystal systems that the $9$ materials predicted by the empirical approach to $0.85$ confidence, and the $6$ materials predicted by all approaches to $0.75$ confidence, may belong to. Four different symmetry categories are observed; cubic, hexagonal, tetragonal and orthorombic. The viewpoints for all materials are down along the $c$-axis.   }
    \label{fig:crystalsystems}
\end{figure}

@@

%histograms 
\begin{figure}[ht]
    \begin{subfigure}[b]{1\textwidth}
    \centering
    \input{figures/histograms/new/LegendHistPaper.tex}
  \end{subfigure}
  \par\bigskip
\begin{subfigure}[b]{0.45\textwidth}
    \input{figures/histograms/new/MP_Eg_count_075.tex}
    \subcaption{}
\end{subfigure}
\begin{subfigure}[b]{0.45\textwidth}
    \input{figures/histograms/new/IonProperty_max ionic char_count_075.tex}
    \subcaption{}
\end{subfigure}%

\begin{subfigure}[b]{0.45\textwidth}
    \input{figures/histograms/new/GeneralizedRDF_std_dev Gaussian center=1.0 width=1.0_count_075.tex}
    \subcaption{}
\end{subfigure}
\begin{subfigure}[b]{0.45\textwidth}
    \input{figures/histograms/new/AverageBondLength_std_dev Average bond length_count_075.tex}
    \subcaption{}
\end{subfigure}
\caption{Histograms of predicted suitable materials as a function of the (a) PBE-calculated band gap from Materials Project, (b) maximum ionic character, (c) standard deviation of the radial distribution function (RDF) and (d) standard deviation of the average bond length. The total number of predicted materials is  $6804$ for the Ferrenti approach, $9227$ for the extended Ferrenti approach, and $214$ for the empirical approach. The Ferrenti and extended Ferrenti approaches refer to the left $y$-axis and the empirical approach to the right.
    }
\label{fig:histogram_new}
\end{figure}

@@

\section*{Additional information}
Correspondence and requests for materials should be addressed to \url{bathen@aps.ee.ethz.ch}.

>>>>

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{physics}
\usepackage{lipsum}
% \usepackage{subfig} %not compatible with subcaption
% \usepackage{braket}
\usepackage{siunitx}
\usepackage{color}
% \usepackage{caption}
\usepackage{subcaption}
\usepackage{tikz,pgfplots}
\usepgfplotslibrary{groupplots,dateplot}
\usetikzlibrary{patterns,shapes.arrows}
\usepackage{makecell}
\captionsetup[table]{skip=10pt}
\pgfplotsset{compat=1.17}
\sisetup{separate-uncertainty}
\usepackage{hyperref}

%\usepackage{longtable}
\usetikzlibrary{patterns,shapes.arrows, arrows.meta,bending, shapes,calc,fadings,decorations.pathreplacing,positioning,arrows.meta}
\pgfplotsset{compat=newest}

@@

%Figure 1 introduction schematic 
\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\textwidth]{AllFigures/ht-workflow-new-2.png}
    \caption{Schematic of an example workflow in material informatics. Results from theory, experiment and computation are fed into material databases (arrow pointing to the center). A cycle involving material screening, machine learning and predictions leads to knowledge gain and ultimately applications in fields such as clean energy and quantum technology. 
    }
    \label{fig:ht-workflow}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\textwidth]{AllFigures/flow_chart_2.png}
    \caption{The project workflow starting from an initial Materials Project (MP) query, and ending with a featurized dataset with entries from several other databases. 
    To limit the memory and computational usage, the data are partitioned into smaller subsets where the respective Pymatgen objects (Pymatgen is a robust, open-source Python library for materials analysis \cite{pymatgen}) are obtained through a query to be used in the following featurization steps. This process is repeated iteratively until all the data has been featurized. \emph{DOS} refers to density of states and \emph{band} to the electronic band structure. 
    }
    \label{fig:flowchart}
\end{figure}

@@

\begin{figure}[t] %!htp
    \centering
    \begin{subfigure}{1\textwidth}
        \centering
        \scalebox{0.85}{\input{AllFigures/01-ferrenti-approach-v2.pgf}}
    \end{subfigure}
    \begin{subfigure}{1\textwidth}
        \centering
          \scalebox{0.85}{\input{AllFigures/02-extended-ferrenti-approach-v3.pgf}}
    \end{subfigure}
    \begin{subfigure}{1\textwidth}
        \centering
          \scalebox{0.85}{\input{AllFigures/03-empirical-approach-v3.pgf}}
    \end{subfigure}
    \caption{Parallel coordinate plots for the different approaches. To limit data cluttering, we have randomly collected up to $250$ entries for each class. For the empirical approach, we have used all the $187$ suitable candidates. The axes show total magnetization (mag), space group (SG), ionic character (ionic char), covalent range (cov range) as calculated from elemental properties, number of elements (num elements) and energy gap (Eg) as extracted from the MP database.} 
    \label{fig:parallel-coordinates-approaches}
\end{figure}

\begin{figure}%[h] %!tbp
    \centering
    \begin{subfigure}{0.35\textwidth}
        \centering
        \includegraphics[width=1\textwidth]{AllFigures/01-ferrenti-approach.pdf}
    \end{subfigure}%
    \begin{subfigure}{0.35\textwidth}
        \centering
        \includegraphics[width=1\textwidth]{AllFigures/02-augmented-ferrenti-approach.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \centering
        \includegraphics[width=1\textwidth]{AllFigures/03-insightful-approach.pdf}
    \end{subfigure}
    \caption{Two-dimensional scatter plots for the three different approaches. We have identified the eigenvectors corresponding to the two largest eigenvalues of the covariance-matrix, that is, the two most important principal components of the initial data from the Materials Project query. Then, we have transformed the sets of labeled data resulting from the three approaches and visualized them as scatter plots. Green squares display suitable candidates, along with the black (SiC), blue (diamond) and yellow (Si) symbols in the bottom panel, and red triangles represent unsuitable candidates.}
    \label{fig:2dscatterplotpca}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \input{AllFigures/01-ferrenti-approach-PC-v2.tex}
        \label{fig:01-fi-e}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \input{AllFigures/01-ferrenti-approach-GB-v2.tex}
        \label{fig:01-fi-d}
    \end{subfigure}%
    \hfill
    \begin{subfigure}[b]{0.45\textwidth}
        \input{AllFigures/03-empirical-approach-PC-v2.tex}
        \label{fig:03-fi-e}
        \subcaption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \input{AllFigures/03-empirical-approach-GB-v2.tex}
        \label{fig:03-fi-d}
        \subcaption{}
    \end{subfigure}
    \caption{Visualization of different parameters for the $25$ most principal components ranked in descending order by (a) the explained variance for the Ferrenti (upper panel) and empirical (lower panel) approaches, and (b) the gradient boosting coefficients for the corresponding approaches. Note that in (a) we visualize only the results of the PCA analysis while in (b) there are results of the PCA reduced training sets using gradient boosting \cite{Hastie2009,xgboost2016}. The latter shows that for the empirical approach most of the physics is represented by a few features. The results in (b) are similar to those obtained with logistic regression, decision trees and random forests.  
    }
    \label{fig:PComponents}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.85\textwidth]{AllFigures/fig6-all.png}
    \caption{Illustrations of the crystal systems that the $9$ materials predicted by the empirical approach to $0.85$ confidence, and the $6$ materials predicted by all approaches to $0.75$ confidence, may belong to. Four different symmetry categories are observed; cubic, hexagonal, tetragonal and orthorombic. The viewpoints for all materials are down along the $c$-axis.   }
    \label{fig:crystalsystems}
\end{figure}

@@

%histograms 
\begin{figure}[ht]
    \begin{subfigure}[b]{1\textwidth}
    \centering
    \input{AllFigures/LegendHistPaper.tex}
  \end{subfigure}
  \par\bigskip
\begin{subfigure}[b]{0.45\textwidth}
    \input{AllFigures/MP_Eg_count_075.tex}
    \subcaption{}
\end{subfigure}
\begin{subfigure}[b]{0.45\textwidth}
% This file was created with tikzplotlib v0.9.16.
\begin{tikzpicture}

\definecolor{color0}{rgb}{0.866666666666667,0.8,0.466666666666667}
\definecolor{color1}{rgb}{0.533333333333333,0.8,0.933333333333333}
\definecolor{color2}{rgb}{0.83921568627451,0.152941176470588,0.156862745098039}
\definecolor{color3}{rgb}{0.8,0.4,0.466666666666667}

\begin{axis}[
height=2.275590092707901in,
legend cell align={left},
legend style={fill opacity=0.8, draw opacity=1, text opacity=1, draw=white!80!black},
tick align=outside,
tick pos=left,
title={},
width=2.8444876158848764in,
x grid style={white!69.0196078431373!black},
xlabel={Max ionic character},
xmin=-0.0460725199741125, xmax=0.967522919456363,
xtick style={color=black},
y grid style={white!69.0196078431373!black},
ylabel={},
ymin=0, ymax=1099.35,
ytick style={color=black}
]
\path [draw=color0, very thick]
(axis cs:0,0)
--(axis cs:0,84)
--(axis cs:0.0484973894464342,84)
--(axis cs:0.0484973894464342,70)
--(axis cs:0.0969947788928685,70)
--(axis cs:0.0969947788928685,72)
--(axis cs:0.145492168339303,72)
--(axis cs:0.145492168339303,74)
--(axis cs:0.193989557785737,74)
--(axis cs:0.193989557785737,134)
--(axis cs:0.242486947232171,134)
--(axis cs:0.242486947232171,93)
--(axis cs:0.290984336678605,93)
--(axis cs:0.290984336678605,237)
--(axis cs:0.33948172612504,237)
--(axis cs:0.33948172612504,195)
--(axis cs:0.387979115571474,195)
--(axis cs:0.387979115571474,183)
--(axis cs:0.436476505017908,183)
--(axis cs:0.436476505017908,240)
--(axis cs:0.484973894464342,240)
--(axis cs:0.484973894464342,164)
--(axis cs:0.533471283910777,164)
--(axis cs:0.533471283910777,464)
--(axis cs:0.581968673357211,464)
--(axis cs:0.581968673357211,190)
--(axis cs:0.630466062803645,190)
--(axis cs:0.630466062803645,176)
--(axis cs:0.678963452250079,176)
--(axis cs:0.678963452250079,314)
--(axis cs:0.727460841696513,314)
--(axis cs:0.727460841696513,387)
--(axis cs:0.775958231142948,387)
--(axis cs:0.775958231142948,1047)
--(axis cs:0.824455620589382,1047)
--(axis cs:0.824455620589382,144)
--(axis cs:0.872953010035816,144)
--(axis cs:0.872953010035816,257)
--(axis cs:0.92145039948225,257)
--(axis cs:0.92145039948225,0);

\path [draw=color1, very thick]
(axis cs:0,0)
--(axis cs:0,21)
--(axis cs:0.0484973894464342,21)
--(axis cs:0.0484973894464342,30)
--(axis cs:0.0969947788928685,30)
--(axis cs:0.0969947788928685,26)
--(axis cs:0.145492168339303,26)
--(axis cs:0.145492168339303,26)
--(axis cs:0.193989557785737,26)
--(axis cs:0.193989557785737,59)
--(axis cs:0.242486947232171,59)
--(axis cs:0.242486947232171,31)
--(axis cs:0.290984336678605,31)
--(axis cs:0.290984336678605,88)
--(axis cs:0.33948172612504,88)
--(axis cs:0.33948172612504,77)
--(axis cs:0.387979115571474,77)
--(axis cs:0.387979115571474,87)
--(axis cs:0.436476505017908,87)
--(axis cs:0.436476505017908,85)
--(axis cs:0.484973894464342,85)
--(axis cs:0.484973894464342,67)
--(axis cs:0.533471283910777,67)
--(axis cs:0.533471283910777,166)
--(axis cs:0.581968673357211,166)
--(axis cs:0.581968673357211,67)
--(axis cs:0.630466062803645,67)
--(axis cs:0.630466062803645,77)
--(axis cs:0.678963452250079,77)
--(axis cs:0.678963452250079,105)
--(axis cs:0.727460841696513,105)
--(axis cs:0.727460841696513,137)
--(axis cs:0.775958231142948,137)
--(axis cs:0.775958231142948,406)
--(axis cs:0.824455620589382,406)
--(axis cs:0.824455620589382,57)
--(axis cs:0.872953010035816,57)
--(axis cs:0.872953010035816,117)
--(axis cs:0.92145039948225,117)
--(axis cs:0.92145039948225,0);

\end{axis}

\begin{axis}[
axis y line=right,
height=2.275590092707901in,
tick align=outside,
width=2.8444876158848764in,
x grid style={white!69.0196078431373!black},
xmin=-0.0460725199741125, xmax=0.967522919456363,
xtick pos=left,
xtick style={color=black},
y grid style={white!69.0196078431373!black},
ymin=0, ymax=17.85,
ytick pos=right,
ytick style={color=color2},
yticklabel style={anchor=west, color=color2}
]
\path [draw=color3, very thick]
(axis cs:0,0)
--(axis cs:0,1)
--(axis cs:0.0484973894464342,1)
--(axis cs:0.0484973894464342,2)
--(axis cs:0.0969947788928685,2)
--(axis cs:0.0969947788928685,0)
--(axis cs:0.145492168339303,0)
--(axis cs:0.145492168339303,0)
--(axis cs:0.193989557785737,0)
--(axis cs:0.193989557785737,2)
--(axis cs:0.242486947232171,2)
--(axis cs:0.242486947232171,1)
--(axis cs:0.290984336678605,1)
--(axis cs:0.290984336678605,4)
--(axis cs:0.33948172612504,4)
--(axis cs:0.33948172612504,6)
--(axis cs:0.387979115571474,6)
--(axis cs:0.387979115571474,3)
--(axis cs:0.436476505017908,3)
--(axis cs:0.436476505017908,1)
--(axis cs:0.484973894464342,1)
--(axis cs:0.484973894464342,0)
--(axis cs:0.533471283910777,0)
--(axis cs:0.533471283910777,4)
--(axis cs:0.581968673357211,4)
--(axis cs:0.581968673357211,3)
--(axis cs:0.630466062803645,3)
--(axis cs:0.630466062803645,5)
--(axis cs:0.678963452250079,5)
--(axis cs:0.678963452250079,4)
--(axis cs:0.727460841696513,4)
--(axis cs:0.727460841696513,4)
--(axis cs:0.775958231142948,4)
--(axis cs:0.775958231142948,17)
--(axis cs:0.824455620589382,17)
--(axis cs:0.824455620589382,2)
--(axis cs:0.872953010035816,2)
--(axis cs:0.872953010035816,10)
--(axis cs:0.92145039948225,10)
--(axis cs:0.92145039948225,0);
\end{axis}

\end{tikzpicture}

    \subcaption{}
\end{subfigure}%

\begin{subfigure}[b]{0.45\textwidth}
% This file was created with tikzplotlib v0.9.16.
\begin{tikzpicture}

\definecolor{color0}{rgb}{0.866666666666667,0.8,0.466666666666667}
\definecolor{color1}{rgb}{0.533333333333333,0.8,0.933333333333333}
\definecolor{color2}{rgb}{0.83921568627451,0.152941176470588,0.156862745098039}
\definecolor{color3}{rgb}{0.8,0.4,0.466666666666667}

\begin{axis}[
height=2.275590092707901in,
legend cell align={left},
legend style={fill opacity=0.8, draw opacity=1, text opacity=1, draw=white!80!black},
tick align=outside,
tick pos=left,
title={},
width=2.8444876158848764in,
x grid style={white!69.0196078431373!black},
xlabel={Std. dev. RDF},
xmin=-0.00174896633573773, xmax=0.0367282930504924,
xtick style={color=black},
y grid style={white!69.0196078431373!black},
ylabel={Number of materials},
ymin=0, ymax=413.2,
ytick style={color=black}
]
\path [draw=color0, very thick]
(axis cs:0,0)
--(axis cs:0,331)
--(axis cs:0.0018410171955134,331)
--(axis cs:0.0018410171955134,291)
--(axis cs:0.00368203439102681,291)
--(axis cs:0.00368203439102681,279)
--(axis cs:0.00552305158654021,279)
--(axis cs:0.00552305158654021,259)
--(axis cs:0.00736406878205362,259)
--(axis cs:0.00736406878205362,231)
--(axis cs:0.00920508597756702,231)
--(axis cs:0.00920508597756702,234)
--(axis cs:0.0110461031730804,234)
--(axis cs:0.0110461031730804,348)
--(axis cs:0.0128871203685938,348)
--(axis cs:0.0128871203685938,355)
--(axis cs:0.0147281375641072,355)
--(axis cs:0.0147281375641072,356)
--(axis cs:0.0165691547596206,356)
--(axis cs:0.0165691547596206,384)
--(axis cs:0.018410171955134,384)
--(axis cs:0.018410171955134,374)
--(axis cs:0.0202511891506474,374)
--(axis cs:0.0202511891506474,310)
--(axis cs:0.0220922063461609,310)
--(axis cs:0.0220922063461609,255)
--(axis cs:0.0239332235416743,255)
--(axis cs:0.0239332235416743,178)
--(axis cs:0.0257742407371877,178)
--(axis cs:0.0257742407371877,105)
--(axis cs:0.0276152579327011,105)
--(axis cs:0.0276152579327011,68)
--(axis cs:0.0294562751282145,68)
--(axis cs:0.0294562751282145,45)
--(axis cs:0.0312972923237279,45)
--(axis cs:0.0312972923237279,28)
--(axis cs:0.0331383095192413,28)
--(axis cs:0.0331383095192413,23)
--(axis cs:0.0349793267147547,23)
--(axis cs:0.0349793267147547,0);

\path [draw=color1, very thick]
(axis cs:0,0)
--(axis cs:0,135)
--(axis cs:0.0018410171955134,135)
--(axis cs:0.0018410171955134,112)
--(axis cs:0.00368203439102681,112)
--(axis cs:0.00368203439102681,101)
--(axis cs:0.00552305158654021,101)
--(axis cs:0.00552305158654021,105)
--(axis cs:0.00736406878205362,105)
--(axis cs:0.00736406878205362,94)
--(axis cs:0.00920508597756702,94)
--(axis cs:0.00920508597756702,117)
--(axis cs:0.0110461031730804,117)
--(axis cs:0.0110461031730804,121)
--(axis cs:0.0128871203685938,121)
--(axis cs:0.0128871203685938,152)
--(axis cs:0.0147281375641072,152)
--(axis cs:0.0147281375641072,147)
--(axis cs:0.0165691547596206,147)
--(axis cs:0.0165691547596206,151)
--(axis cs:0.018410171955134,151)
--(axis cs:0.018410171955134,131)
--(axis cs:0.0202511891506474,131)
--(axis cs:0.0202511891506474,120)
--(axis cs:0.0220922063461609,120)
--(axis cs:0.0220922063461609,85)
--(axis cs:0.0239332235416743,85)
--(axis cs:0.0239332235416743,61)
--(axis cs:0.0257742407371877,61)
--(axis cs:0.0257742407371877,31)
--(axis cs:0.0276152579327011,31)
--(axis cs:0.0276152579327011,22)
--(axis cs:0.0294562751282145,22)
--(axis cs:0.0294562751282145,15)
--(axis cs:0.0312972923237279,15)
--(axis cs:0.0312972923237279,6)
--(axis cs:0.0331383095192413,6)
--(axis cs:0.0331383095192413,8)
--(axis cs:0.0349793267147547,8)
--(axis cs:0.0349793267147547,0);
\end{axis}

\begin{axis}[
axis y line=right,
height=2.275590092707901in,
tick align=outside,
width=2.8444876158848764in,
x grid style={white!69.0196078431373!black},
xmin=-0.00174896633573773, xmax=0.0367282930504924,
xtick pos=left,
xtick style={color=black},
y grid style={white!69.0196078431373!black},
ymin=0, ymax=13.65,
ytick pos=right,
ytick style={color=color2},
yticklabel style={anchor=west, color=color2}
]
\path [draw=color3, very thick]
(axis cs:0,0)
--(axis cs:0,6)
--(axis cs:0.0018410171955134,6)
--(axis cs:0.0018410171955134,3)
--(axis cs:0.00368203439102681,3)
--(axis cs:0.00368203439102681,5)
--(axis cs:0.00552305158654021,5)
--(axis cs:0.00552305158654021,3)
--(axis cs:0.00736406878205362,3)
--(axis cs:0.00736406878205362,2)
--(axis cs:0.00920508597756702,2)
--(axis cs:0.00920508597756702,2)
--(axis cs:0.0110461031730804,2)
--(axis cs:0.0110461031730804,6)
--(axis cs:0.0128871203685938,6)
--(axis cs:0.0128871203685938,4)
--(axis cs:0.0147281375641072,4)
--(axis cs:0.0147281375641072,5)
--(axis cs:0.0165691547596206,5)
--(axis cs:0.0165691547596206,13)
--(axis cs:0.018410171955134,13)
--(axis cs:0.018410171955134,4)
--(axis cs:0.0202511891506474,4)
--(axis cs:0.0202511891506474,6)
--(axis cs:0.0220922063461609,6)
--(axis cs:0.0220922063461609,5)
--(axis cs:0.0239332235416743,5)
--(axis cs:0.0239332235416743,1)
--(axis cs:0.0257742407371877,1)
--(axis cs:0.0257742407371877,1)
--(axis cs:0.0276152579327011,1)
--(axis cs:0.0276152579327011,2)
--(axis cs:0.0294562751282145,2)
--(axis cs:0.0294562751282145,0)
--(axis cs:0.0312972923237279,0)
--(axis cs:0.0312972923237279,0)
--(axis cs:0.0331383095192413,0)
--(axis cs:0.0331383095192413,1)
--(axis cs:0.0349793267147547,1)
--(axis cs:0.0349793267147547,0);
\end{axis}

\end{tikzpicture}

    \subcaption{}
\end{subfigure}
\begin{subfigure}[b]{0.45\textwidth}
% This file was created with tikzplotlib v0.9.16.
\begin{tikzpicture}

\definecolor{color0}{rgb}{0.866666666666667,0.8,0.466666666666667}
\definecolor{color1}{rgb}{0.533333333333333,0.8,0.933333333333333}
\definecolor{color2}{rgb}{0.83921568627451,0.152941176470588,0.156862745098039}
\definecolor{color3}{rgb}{0.8,0.4,0.466666666666667}

\begin{axis}[
height=2.275590092707901in,
legend cell align={left},
legend style={fill opacity=0.8, draw opacity=1, text opacity=1, draw=white!80!black},
tick align=outside,
tick pos=left,
title={},
width=2.8444876158848764in,
x grid style={white!69.0196078431373!black},
xlabel={Std. dev. average bond length},
xmin=-0.0263144046185111, xmax=0.838491250528538,
xtick style={color=black},
y grid style={white!69.0196078431373!black},
ylabel={},
ymin=0, ymax=732.9,
ytick style={color=black}
]
\path [draw=color0, very thick]
(axis cs:0.0129949433427184,0)
--(axis cs:0.0129949433427184,28)
--(axis cs:0.0543732043545389,28)
--(axis cs:0.0543732043545389,65)
--(axis cs:0.0957514653663595,65)
--(axis cs:0.0957514653663595,156)
--(axis cs:0.13712972637818,156)
--(axis cs:0.13712972637818,279)
--(axis cs:0.178507987390001,279)
--(axis cs:0.178507987390001,403)
--(axis cs:0.219886248401821,403)
--(axis cs:0.219886248401821,468)
--(axis cs:0.261264509413642,468)
--(axis cs:0.261264509413642,590)
--(axis cs:0.302642770425462,590)
--(axis cs:0.302642770425462,698)
--(axis cs:0.344021031437283,698)
--(axis cs:0.344021031437283,563)
--(axis cs:0.385399292449103,563)
--(axis cs:0.385399292449103,445)
--(axis cs:0.426777553460924,445)
--(axis cs:0.426777553460924,340)
--(axis cs:0.468155814472744,340)
--(axis cs:0.468155814472744,193)
--(axis cs:0.509534075484565,193)
--(axis cs:0.509534075484565,118)
--(axis cs:0.550912336496385,118)
--(axis cs:0.550912336496385,52)
--(axis cs:0.592290597508206,52)
--(axis cs:0.592290597508206,31)
--(axis cs:0.633668858520026,31)
--(axis cs:0.633668858520026,18)
--(axis cs:0.675047119531847,18)
--(axis cs:0.675047119531847,11)
--(axis cs:0.716425380543667,11)
--(axis cs:0.716425380543667,6)
--(axis cs:0.757803641555488,6)
--(axis cs:0.757803641555488,2)
--(axis cs:0.799181902567308,2)
--(axis cs:0.799181902567308,0);

\path [draw=color1, very thick]
(axis cs:0.0129949433427184,0)
--(axis cs:0.0129949433427184,13)
--(axis cs:0.0543732043545389,13)
--(axis cs:0.0543732043545389,36)
--(axis cs:0.0957514653663595,36)
--(axis cs:0.0957514653663595,68)
--(axis cs:0.13712972637818,68)
--(axis cs:0.13712972637818,111)
--(axis cs:0.178507987390001,111)
--(axis cs:0.178507987390001,166)
--(axis cs:0.219886248401821,166)
--(axis cs:0.219886248401821,190)
--(axis cs:0.261264509413642,190)
--(axis cs:0.261264509413642,243)
--(axis cs:0.302642770425462,243)
--(axis cs:0.302642770425462,257)
--(axis cs:0.344021031437283,257)
--(axis cs:0.344021031437283,205)
--(axis cs:0.385399292449103,205)
--(axis cs:0.385399292449103,143)
--(axis cs:0.426777553460924,143)
--(axis cs:0.426777553460924,119)
--(axis cs:0.468155814472744,119)
--(axis cs:0.468155814472744,70)
--(axis cs:0.509534075484565,70)
--(axis cs:0.509534075484565,29)
--(axis cs:0.550912336496385,29)
--(axis cs:0.550912336496385,16)
--(axis cs:0.592290597508206,16)
--(axis cs:0.592290597508206,20)
--(axis cs:0.633668858520026,20)
--(axis cs:0.633668858520026,7)
--(axis cs:0.675047119531847,7)
--(axis cs:0.675047119531847,4)
--(axis cs:0.716425380543667,4)
--(axis cs:0.716425380543667,3)
--(axis cs:0.757803641555488,3)
--(axis cs:0.757803641555488,0)
--(axis cs:0.799181902567308,0)
--(axis cs:0.799181902567308,0);

\end{axis}

\begin{axis}[
axis y line=right,
height=2.275590092707901in,
tick align=outside,
width=2.8444876158848764in,
x grid style={white!69.0196078431373!black},
xmin=-0.0263144046185111, xmax=0.838491250528538,
xtick pos=left,
xtick style={color=black},
y grid style={white!69.0196078431373!black},
ymin=0, ymax=12.6,
ytick pos=right,
ytick style={color=color2},
yticklabel style={anchor=west, color=color2}
]
\path [draw=color3, very thick]
(axis cs:0.0129949433427184,0)
--(axis cs:0.0129949433427184,2)
--(axis cs:0.0543732043545389,2)
--(axis cs:0.0543732043545389,3)
--(axis cs:0.0957514653663595,3)
--(axis cs:0.0957514653663595,1)
--(axis cs:0.13712972637818,1)
--(axis cs:0.13712972637818,5)
--(axis cs:0.178507987390001,5)
--(axis cs:0.178507987390001,6)
--(axis cs:0.219886248401821,6)
--(axis cs:0.219886248401821,10)
--(axis cs:0.261264509413642,10)
--(axis cs:0.261264509413642,7)
--(axis cs:0.302642770425462,7)
--(axis cs:0.302642770425462,12)
--(axis cs:0.344021031437283,12)
--(axis cs:0.344021031437283,7)
--(axis cs:0.385399292449103,7)
--(axis cs:0.385399292449103,7)
--(axis cs:0.426777553460924,7)
--(axis cs:0.426777553460924,4)
--(axis cs:0.468155814472744,4)
--(axis cs:0.468155814472744,4)
--(axis cs:0.509534075484565,4)
--(axis cs:0.509534075484565,0)
--(axis cs:0.550912336496385,0)
--(axis cs:0.550912336496385,1)
--(axis cs:0.592290597508206,1)
--(axis cs:0.592290597508206,0)
--(axis cs:0.633668858520026,0)
--(axis cs:0.633668858520026,0)
--(axis cs:0.675047119531847,0)
--(axis cs:0.675047119531847,0)
--(axis cs:0.716425380543667,0)
--(axis cs:0.716425380543667,0)
--(axis cs:0.757803641555488,0)
--(axis cs:0.757803641555488,0)
--(axis cs:0.799181902567308,0)
--(axis cs:0.799181902567308,0);
\end{axis}

\end{tikzpicture}

    \subcaption{}
\end{subfigure}
\caption{Histograms of predicted suitable materials as a function of the (a) PBE-calculated band gap from Materials Project, (b) maximum ionic character, (c) standard deviation of the radial distribution function (RDF) and (d) standard deviation of the average bond length. The total number of predicted materials is  $6804$ for the Ferrenti approach, $9227$ for the extended Ferrenti approach, and $214$ for the empirical approach. The Ferrenti and extended Ferrenti approaches refer to the left $y$-axis and the empirical approach to the right.
    }
\label{fig:histogram_new}
\end{figure}

@@

\section*{Additional information}
Correspondence and requests for materials should be addressed to \url{bathen@aps.ee.ethz.ch}. Supplementary material is available at \url{https://github.com/mhjensen/PredictingSolidStateQubitCandidates}.
